Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-15 paper/arxiv/supp_3_ml.tex
import SI section 2.2

>>>>

\cref{supp_fig19:pairwise_eads_des} displays the pairwise relationships between CO adsorption energy
and its four most correlated descriptors: d-band center (spin-up) $\delta\epsilon_{\text{d}}\uparrow$,
lattice parameter $\gamma$, vacuum level $E_\text{vac}$, and electronegativity
on the Allen scale $\chi_\text{Allen}$, identified by Kendall rank correlation analysis.
\cref{supp_table15:descriptor_notations} lists notations for elementary descriptors and electronic descriptors.
